\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

\def\name{Eric DeMoney}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
%\def\footerlink{http://jblevins.org/projects/cv-template/}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {TCP, UDP, mathematics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={7in, 11in},
  left=0.75in,
  right=0.75in,
  top=0.75in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

% \vspace{0.15in}

\begin{minipage}{0.475\linewidth}
   Recent Computer Science graduate with significant experience with C++, mobile, and web development with proven ability to quickly learn new skills and languages. 
\end{minipage}
\hspace{0.125cm}
\begin{minipage}{0.475\linewidth}
  \begin{tabular}{ll}
    Location: & Chico CA, willing to relocate\\
    Phone: & (408) 406-3025\\
    Email: & \href{mailto:eric@demoney.net}{\tt eric@demoney.net}\\
    Github: & \href{https://github.com/erdemoney}{\tt github.com/erdemoney}\\
  \end{tabular}
\end{minipage}

\vspace{0.2in}

\begin{minipage}[t]{0.475\linewidth}
    \section*{Education}
    \begin{itemize}
    \item[$\bullet$] B.S. Computer Science, December 2021\\
        California State University, Chico
    \end{itemize}
    \section*{Relevant Courses}
    \begin{itemize}
        \item[$\bullet$] CSCI 567 Mobile Application Development
        \item[$\bullet$] CSCI 430 Software Engineering
        \item[$\bullet$] CSCI 551 Numerical Methods and Parallel\\Programming
        \item[$\bullet$] CSCI 111, 211, 311, 550 Programming and\\Algorithms
        \item[$\bullet$] MATH 314 Probability And Statistics For Science And Technology
    \end{itemize}
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[t]{0.475\linewidth}
    \section*{Technical Skills}
    \subsection*{Languages and Frameworks}
    \begin{itemize}
        \item[$\bullet$] \emph{Proficient with} C++, Flutter/Dart, and Django
        \item[$\bullet$] \emph{Familiar with} C, Python, R, Java, JavaScript, HTML/CSS, SQL, Powershell and Bash
        \item[$\bullet$] \emph{Learning} Go and TensorFlow
    \end{itemize}
    \subsection*{Software}
    \begin{itemize}
        \item[$\bullet$] Git, GDB, Valgrind, Firebase
        \item[$\bullet$] Unix command line tools
        \item[$\bullet$] Active Directory
        \item[$\bullet$] 4 years of Linux experience
    \end{itemize}
\end{minipage}

\section*{Experience}
\subsection*{Information Security Intern Enloe Medical Center, Chico, CA, August 2018 - August 2019
}
\begin{itemize}
    \item[$\bullet$] Automated user creation and termination processes saving \textasciitilde 6 hours of work per week and eliminating the need to purchase expensive provisioning software.
 \item[$\bullet$] Developed scripts to generate Excel spreadsheets of vital security metrics for weekly review.
 \item[$\bullet$] Secretary of Risk Management Committee, which discusses solutions for high-risk vulnerabilities in the\\hospital's technical infrastructure.
 \item[$\bullet$] Performed daily tasks such as log monitoring using Proofpoint, LogRhythm, and Rapid7.
 \item[$\bullet$] Maintained extensive technical documentation for scripts and programs developed.
\end{itemize}
\subsection*{Projects}
\begin{itemize}
    \item[$\bullet$] Developed website that allows friends to discuss and vote on what restaurant to go to using results from Yelp. \emph{Implemented using the Django web framework, WebSockets, Yelp API and Bootstrap front-end toolkit.}
    \item[$\bullet$] Developed cross-platform mobile application for collaboratively planning outdoors trips with friends.\\\emph{Implemented using the Flutter SDK, Firebase Realtime Database, Google Places API, and OpenWeatherMap API.}
    \item[$\bullet$] Implemented Minesweeper solving algorithm and Minesweeper game in C++.
    \item[$\bullet$] Implemented compiler/interpreter in C++ for a programming language for making OpenGL computer games.
    \item[$\bullet$] Wrote network file transfer utility with error correction in C using the Berkeley sockets API.
    \item[$\bullet$] Currently working on designing an application to identify and catalog fish species captured by underwater cameras on the Yuba River using the TensorFlow Object Detection API.
\end{itemize}
\end{document}
